A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2017-07-17 meth.tex
update decision tree figure, update all result graphs with y axis 0

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{decision_tree.png}
    \caption[]{
      \label{fig:decision_tree}
      The default method decision tree used in the \code{aneris} software
% * <maarten.vandenberg@pbl.nl> 2017-07-03T21:40:43.868Z:
% 
% > The default method decision tree
% yes and no might be added to the tree for improved clarity. 
% 
% ^.
      library. For all decisions, upper branches represent a ``yes'' response
      and lower branches represent a ``no'' response. $dH$ is defined as
      $\left|\frac{h(t_i) - m(t_i)}{h(t_i)}\right|$, and decision-making
      thresholds for $c_v$ and $dH$ are described below. Methods labeled in
      \textit{green} are likely to closely match unharmonized results, methods
      in \textit{yellow} will likely somewhat match unharmonized results, and
      methods in \textit{red} can be expected to have a large relative
      difference between harmonized and unharmonized results.}
  \end{center}
\end{figure}

@@

The value of $c_v$ is then tested against a threshold, $\tau_{c_v}$. To
determine this threshold, an analysis of the recent CEDS and LUC historical data
has been performed. Figure \ref{fig:cov} shows the distribution of LUC $c_v$s
and non-LUC $c_v$s as determined for historical data aggregated to the model
regions of 5 different IAMs involved in the SSP process. A threshold value of
$c_v < \tau_{c_v} = 20$ has been chosen based on these observations as it
optimally divides the two distributions. Importantly, tails of the LUC and
non-LUC overlap, thus there are both false positives (~7\% of non-LUC
trajectories) and false negatives (~10\% of LUC trajectories). However, as any
regional definition is model dependent and thus any regional aggregation is
possible an automated detection mechanism is necessary.

@@

Finally, consideration is taken with respect to the relative difference between
the historic and model values in the harmonization time period. In order to
investigate the possible values that these relative differences can take, the
IAM values used in the SSP and (ongoing) CMIP6 inter-comparison
exercises are used. A distribution of these differences for all models in the
study is presented in Figure \ref{fig:dh}. Given the available data, a threshold
value of $dH < \tau_{dH} = 50$\% was chosen to be used as a default in \code{aneris}.
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:25:47.452Z:
% 
% > 50\%
% What does this mean? I would expect something of the form low_value < dH < high_value?
% 
% ^.

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=\textwidth]{decision_tree.png}
    \caption[]{
      \label{fig:decision_tree}
      The default method decision tree used in the \code{aneris} software
      library. For all decisions, upper (purple) branches represent a ``yes''
      response and lower (orange) branches represent a ``no'' response. $dH$ is
      defined as $\left|\frac{h(t_i) - m(t_i)}{h(t_i)}\right|$, and
      decision-making thresholds for $c_v$ and $dH$ are described below. Methods
      labeled in \textit{green} are likely to closely match unharmonized
      results, methods in \textit{yellow} will likely somewhat match
      unharmonized results, and methods in \textit{red} can be expected to have
      a large relative difference between harmonized and unharmonized results.}
  \end{center}
\end{figure}

@@

The value of $c_v$ is then tested against a threshold, $\tau_{c_v}$. To
determine this threshold, an analysis of the recent CEDS and LUC historical data
has been performed. Figure \ref{fig:cov} shows the distribution of LUC $c_v$s
and non-LUC $c_v$s as determined for historical data aggregated to the model
regions of 5 different IAMs involved in the SSP process. A threshold value of
$\tau_{c_v} = 20$ has been chosen based on these observations as it
optimally divides the two distributions. Importantly, tails of the LUC and
non-LUC overlap, thus there are both false positives (~7\% of non-LUC
trajectories) and false negatives (~10\% of LUC trajectories). However, as any
regional definition is model dependent and thus any regional aggregation is
possible an automated detection mechanism is necessary.

@@

Finally, consideration is taken with respect to the relative difference between
the historic and model values in the harmonization time period. In order to
investigate the possible values that these relative differences can take, the
IAM values used in the SSP and (ongoing) CMIP6 inter-comparison
exercises are used. A distribution of these differences for all models in the
study is presented in Figure \ref{fig:dh}. Given the available data, a threshold
value of $\tau_{dH} = 50$\% was chosen to be used as a default in \code{aneris}.
% * <maarten.vandenberg@pbl.nl> 2017-07-03T22:25:47.452Z:
% 
% > 50\%
% What does this mean? I would expect something of the form low_value < dH < high_value?
% 
% ^.
